Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-21 Manuscript.Rmd

```
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

##Replication Demographic Analaysis
##Age Analysis
```{r}
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
BLS_age <- read_excel("age_demo.xlsx")

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
```
###Education Analysis 
```{r}
#Education Analysis 
#Clean BLS Data. Get totals.  
BLS_education_original <- read_excel("education_demo.xlsx")
BLS_education <- as.data.frame(BLS_education_original[8:14, ])
BLS_education <- BLS_education[1, c(-2, -3, -6)]
names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")

@@

>>>>

##Replication Demographic Analaysis
##Age Analysis
```{r}
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
age_demo <- read_excel("age_demo.xlsx")

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
```

###Education Analysis 
```{r}
#Education Analysis 
#Clean BLS Data. Get totals.  
BLS_education_original <- read_excel("education_demo.xlsx")
BLS_education <- as.data.frame(BLS_education_original[8:14, ])
BLS_education <- BLS_education[1, c(-2, -3, -6)]
names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")

@@

```
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
=======
